Graph-Based Neural Reconstruction \\ from Skeletonized 3D Networks

### 2017-11-15 papers/cvpr2018/2_method.tex
paper: updated figures and addressed HP comments

First, we extract a skeleton from each segment in the label volume using the TEASER algorithm~\cite{sato2000teasar,zhao2014automatic}. Fig.~\ref{fig:skeletonization} shows an example of two extracted skeletons (in black). These skeletons consist of a sequence of \textit{joints}, i.e., locations that are locally a maximum distance from the segment boundary, with line segments connecting successive joints. We prune the joints that are within $t_{jnt} = 50$ voxels of each other to reduce unnecessary branching. We refer to joints that have only one connected neighbor as \textit{endpoints}. Many of the segments that are erroneously split have nearby endpoints  (Fig.~\ref{fig:merge_candidates}). We make use of this fact to merge segments with the following two-pass pruning algorithm.

In the first pass, we iterate over all endpoints $e$ belonging to a segment $S$ and create a set of segments $\mathbb{S}_e^\prime$ that includes all labels that are within $t_{low}$ voxels from $e$. Elements of $\mathbb{S}_e^\prime$ are candidates for merging. However, this first pass often leads to too many candidates, requiring an additional pass for further pruning. In the second pass, we consider all of the segments in $\mathbb{S}_e^\prime$ for every endpoint $e$. If a segment $S^\prime \in \mathbb{S}_e^\prime$ has an endpoint within $t_{high}$ voxels of $e$, the segment $S$ and $S^\prime$ are considered for merging. We store the midpoints between the two endpoints as the center of the potential merges in the set $\mathbb{S}_c$.
\hp{add how the final graph is constructed}

\begin{figure}[t]
	\centering
	\includegraphics[width=0.92\linewidth]{./figures/split_error1.png}
	\includegraphics[width=0.92\linewidth]{./figures/split_error2.png}
	\caption{Two erroneously split segments.}
	\label{fig:merge_candidates}
\end{figure}

\subsection{Edge Weights Assignment}
We assign non-negative edge weights $w_e$ to each edge where the weight corresponds to the probability that two nodes belong to the same neuron.
Instead of using handcrafted features to compute the similarity between adjacent nodes, we train a 3D CNN classifier to learn from the manually labeled oversegmentation input volume (Sec.~\ref{sec:dataset}).
%Our  edge weights  correspond to probabilities that two endpoints $e$ in $\mathbb{S}_c$ belong to the same neuron and should be merged. \hp{check}

>>>>

First, we extract a skeleton from each segment in the label volume using the TEASER algorithm~\cite{sato2000teasar,zhao2014automatic}. Fig.~\ref{fig:skeletonization} shows an example of two extracted skeletons (in black). These skeletons consist of a sequence of \textit{joints}, i.e., locations that are locally a maximum distance from the segment boundary, with line segments connecting successive joints. We prune the joints that are within $t_{jnt} = 50$ voxels of each other to reduce unnecessary branching. We refer to joints that have only one connected neighbor as \textit{endpoints}. Many of the segments that are erroneously split have nearby endpoints  (Fig.~\ref{fig:merge_candidates}). We make use of this fact to find merge candidates with the following two-pass pruning algorithm.

In the first pass, we iterate over all endpoints $e$ belonging to a segment $S$ and create a set of segments $\mathbb{S}_e^\prime$ that includes all labels that are within $t_{low}$ voxels from $e$. Elements of $\mathbb{S}_e^\prime$ are candidates for merging. However, this first pass often leads to too many candidates, requiring an additional pass for further pruning. In the second pass, we consider all of the segments in $\mathbb{S}_e^\prime$ for every endpoint $e$. If a segment $S^\prime \in \mathbb{S}_e^\prime$ has an endpoint within $t_{high}$ voxels of $e$, the segment $S$ and $S^\prime$ are considered for merging. We store the midpoints between the two endpoints as the center of the potential merges in the set $\mathbb{S}_c$. This algorithm produces a set of segments to consider for merging. Only these pairs have a corresponding edge in the constructed graph.

\begin{figure}[t]
	\centering
	\includegraphics[width=0.92\linewidth]{./figures/split_error1.png}
	\includegraphics[width=0.92\linewidth]{./figures/split_error2.png}		\includegraphics[width=0.85\linewidth]{./figures/merge_candidate2.png}
	\caption{Three erroneously split segments.}
	\label{fig:merge_candidates}
\end{figure}

\subsection{Edge Weights Assignment}
We assign edge weights $w_e$ to each edge where the weight corresponds to the probability that two nodes belong to the same neuron.
Instead of using handcrafted features to compute the similarity between adjacent nodes, we train a 3D CNN classifier to learn from the manually labeled oversegmentation input volume (Sec.~\ref{sec:dataset}).
If the probability of the nodes belonging to the same neuron is $p_e$, the edge weight $w_e = \log{\frac{p_e}{1 - p_e}} + \log{\frac{1 - \beta}{\beta}}$, where $\beta$ is a tunable parameter that encourages over or undersegmentation.
%Our  edge weights  correspond to probabilities that two endpoints $e$ in $\mathbb{S}_c$ belong to the same neuron and should be merged. \hp{check}

### 2017-11-15 papers/cvpr2018/3_evaluation.tex
major updates to paper figures
paper: updated figures and addressed HP comments

\paragraph{Kasthuri.}
The Kasthuri dataset consists of scanning electron microscope images of the neocortex of a mouse brain~\cite{kasthuri2015saturated}. This dataset is $5342 \times 3618 \times 338$ voxels in size. The resolution of the dataset is $\SI[product-units=single]{3 x 3 x 30}{\nano\meter}^3$ per voxel. We evaluate our methods using the left cylinder of this 3-cylinder dataset. We downsample the dataset in the $x$ and $y$ dimensions to give a final resolution of $\SI[product-units=single]{6 x 6 x 30}{\nano\meter}^3$ per voxel. We divide the dataset into two volumes (Vol. 1 and Vol. 2) along the $x$ dimension, where each volume is $\SI[product-units=single]{8.0 x 10.9 x 10.1}{\micro\meter}^3$ or $X \times Y \times Z$ voxels. \hp{add voxels}

@@

The segmentation on the Kasthuri dataset was computed by agglomerating 3D supervoxels produced by the z-watershed algorithm from 3D affinity predictions~\cite{zlateski2015image}. A recent study by Funke et al.~\cite{schlegel2017learning} demonstrated superior performance of such methods over existing ones on anisotropic data. We learn 3D affinities using MALIS loss with a U-net~\cite{Turaga:2009,ronneberger2015u}. We apply the z-watershed algorithm with suitable parameters to compute a 3D oversegmentation of the volume. The resulting 3D oversegmentation is then agglomerated using the technique of context-aware delayed agglomeration to generate the final segmentation~\cite{10.1371/journal.pone.0125825}.

>>>>

\paragraph{Kasthuri.}
The Kasthuri dataset consists of scanning electron microscope images of the neocortex of a mouse brain~\cite{kasthuri2015saturated}. This dataset is $5342 \times 3618 \times 338$ voxels in size. The resolution of the dataset is $\SI[product-units=single]{3 x 3 x 30}{\nano\meter}^3$ per voxel. We evaluate our methods using the left cylinder of this 3-cylinder dataset. We downsample the dataset in the $x$ and $y$ dimensions to give a final resolution of $\SI[product-units=single]{6 x 6 x 30}{\nano\meter}^3$ per voxel. We divide the dataset into two volumes (Vol. 1 and Vol. 2) along the $x$ dimension, where each volume is $\SI[product-units=single]{8.0 x 10.9 x 10.1}{\micro\meter}^3$ or $1335 \times 1809 \times 338$ voxels.

@@

The segmentation on the Kasthuri dataset was computed by agglomerating 3D supervoxels produced by the z-watershed algorithm from 3D affinity predictions~\cite{zlateski2015image}. A recent study by Funke et al.~\cite{schlegel2017learning} demonstrated superior performance of such methods over existing ones on anisotropic data. We learn 3D affinities using MALIS loss with a U-net~\cite{ronneberger2015u,Turaga:2009}. We apply the z-watershed algorithm with suitable parameters to compute a 3D oversegmentation of the volume. The resulting 3D oversegmentation is then agglomerated using the technique of context-aware delayed agglomeration to generate the final segmentation~\cite{10.1371/journal.pone.0125825}.

### 2017-11-15 papers/cvpr2018/4_results.tex
paper: updated figures and addressed HP comments

In Fig.~\ref{fig:variation-of-information}, we show the VI results of the pixel-based reconstructions of the Kasthuri and FlyEM data (Sec.~\ref{sec:neuroproof}) for varying thresholds of agglomeration (green). We use one of these segmentations (green circle) as out input dataset with an agglomeration threshold of 0.3 for all datasets. The results from our method are shown in red for varying X \hp{add} parameters. We show comparisons to an oracle (blue) that correctly partitions the graph from our method based on ground truth.

@@

Equally important is the number of split errors that remain after pruning. These are the locations that we want to merge to create a more accurate reconstructions. For every dataset, the number of true split errors remains constant before and after pruning. \hp{not sure what you mean}
However, since our heuristic does not enforce an adjacency constraint of two regions when constructing edges in the graph, the difference does not indicate the number of examples excluded by pruning. Fig.~\ref{fig:skeleton-results} shows an example segment with a split error (green segment) that our algorithm missed. Of the successful examples in Fig.~\ref{fig:positive-results}, the second and fourth groupings contain pairs of non-adjacent segments that were merged by our method. \hp{this paragraph needs more work to make it clearer}

\begin{figure}[h!]
	\centering
	\includegraphics[width=0.85\linewidth]{./figures/merge_candidate1.png}
	\includegraphics[width=0.85\linewidth]{./figures/merge_candidate2.png}
	\caption{Example merge candidates.}
	\label{fig:skeleton-results}
\end{figure}

@@

The graph optimization strategy using multicut increases our accuracy over using just the CNN.
Table \ref{table:multicut} shows the changes in precision, recall, and accuracy for all four datasets compared to the CNN.
The precision increases on each dataset, although the recall decreases on all but one of the datasets.
Since it is more difficult to correct merge errors than split errors, it is often desirable to sacrifice recall for precision.
Over the three testing datasets, applying a graph-based partitioning strategy reduced the number of merge errors by \FIX{X}, \FIX{Y}, and \FIX{Z}, respectively. \hp{would be good to show the actual precision / recall numbers, too (at least in supplemental). maybe swap the ROC figure with a precision /recall figure?}

>>>>

In Fig.~\ref{fig:variation-of-information}, we show the VI results of the pixel-based reconstructions of the Kasthuri and FlyEM data (Sec.~\ref{sec:neuroproof}) for varying thresholds of agglomeration (green). We use one of these segmentations (green circle) as out input dataset with an agglomeration threshold of 0.3 for all datasets. The results from our method are shown in red for varying the $\beta$ parameter. We show comparisons to an oracle (blue) that correctly partitions the graph from our method based on ground truth.

@@

We generate edges in our graph by using information from the skeletons. 
In particular, we do not enforce the constraint that edges in our graph correspond to adjacent segments.
Although neurons are continuous, the EM images often have noisy spots which cause a break in the input segmentation.
We still want to reconstruct these neurons despite the fact that the initial segmentation is non-continuous. 
The second and fourth examples in Fig.~\ref{fig:positive-results} show correctly reconstructed neurons where two of the segments are non-adjacent. 
This is a large benefit over enforcing segment adjacency.

There are some pairs of segments which we do not consider for merging because of our reliance on the skeletons. 
Fig.~\ref{fig:skeleton-results} shows such an example segment that our algorithm missed. 
The endpoints of both segments are circled.
In this example the small segment is carved from the larger segment in a location where there are no skeleton endpoints.

\begin{figure}[h!]
	\centering
	\includegraphics[width=0.85\linewidth]{./figures/merge_candidate1.png}
	\caption{Example merge candidates.}
	\label{fig:skeleton-results}
\end{figure}

@@

The graph optimization strategy using multicut increases our accuracy over using just the CNN.
Table \ref{table:multicut} shows the changes in precision, recall, and accuracy for all four datasets compared to the CNN.
The precision increases on each dataset, although the recall decreases on all but one of the datasets.
Since it is more difficult to correct merge errors than split errors, it is often desirable to sacrifice recall for precision.
Over the three testing datasets, applying a graph-based partitioning strategy reduced the number of merge errors by \FIX{X}, \FIX{Y}, and \FIX{Z}, respectively.
